### 2012-05-19 trunk/GUIErrorDetector/paper/evaluation.tex
correct typo
margin change

\end{center}
\vspace{-15pt}
\Caption{{\label{table:subjects} Open-source programs
used in our evaluation. Column ``LOC'' is the number of non-blank, non-comment lines
of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
together with its GUI framework, as listed in
the bottom table.} }
\end{table}

@@

\subsection{Experimental Procedure}
\label{sec:procedural}

We ran our tool on each subject with three call graph construction
algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
each call graph construction algorithm on three Android applications, we
used two configurations: with and without our enhancements
(Section~\ref{sec:cgcon}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
because they do not scale to our subject programs.

Subject SGTPuzzler uses native methods to interact with
the underlying operating system. For it, we manually checked the possible
Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
annotations for it. 
Two subjects (MyTracks and Fennec)
use a customized pattern to interact with the GUI framework.
For them, we added \filternum user-defined filters, described in Section~\ref{sec:heuristic}.
In this experiment, none of the paper
authors was familiar with the subjects, but we found it was quite easy
to add extra annotations and user-defined filters. All these
manual parts took less than a total of 60 minutes.

@@

\tinystep
\subsection{Results}
\label{sec:results}

@@

\subsubsection{Errors in Multithreaded GUI Applications}
\label{sec:errors}

As shown in Table~\ref{table:results}, our tool found
errors in each subject. Using the 1-CFA
call graph algorithm, our tool issued \warnings warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown,
and the \oldbugs known errors were correctly identified),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

We submitted all \newbugs new errors to the respective developers. As of May 2012, 
1 error S3dropbox has been confirmed, and we have reproduced other errors.
All found bugs and our experimental results are
publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
%in which 2 errors in FileBunker and ArecaBackup
%have not yet been verified by the developers. 
%2 errors in SudokuSolver can be reproduced by simply
%clicking its UIs, and the rest 4 errors can be reproduced
%by writing a test driver have not yet been verified
%by the developers.

@@

77.private void deleteError() \ttlcb
78.    String text = "Cannot delete folder .....";
79.    display.showErrorMessage("Delete failed", 
        String.format(text, controller.getSelectedBucketName())); 
80.\ttrcb
\end{alltt}
\end{CodeOut}
\vspace*{-15pt}
\Caption{{\label{fig:swingerror} An
invalid thread access error reported by our tool
in the S3dropbox Swing application. The error occurs when
the method \CodeIn{deleteCurrentBucket} invoked on line 63 throws
an exception, which causes method \CodeIn{deleteError} to
access a Swing GUI object \CodeIn{display} on line 79 from
a non-UI thread. This error was previously unknown, and has been confirmed by the S3dropbox developers.
}} %\vspace{-5mm}
\end{figure}

@@

\subsubsection{Comparison to Requiring Wrappers}
\label{sec:straightforward}

>>>>

\end{center}
\vspace{-15pt}
\Caption{{\label{table:subjects} Open-source programs
used in our evaluation. Column ``LOC'' is the number of lines
of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
together with its GUI framework, as listed in
the bottom table.}} 
\end{table}

@@

%\vspace{2mm}
\vspace{-3mm}
\subsection{Experimental Procedure}
\label{sec:procedural}

We ran our tool on each subject program with three call graph construction
algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
each call graph construction algorithm on three Android applications, we
used two configurations: with and without our enhancements
(Section~\ref{sec:cgcon}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
because they do not scale to our subject programs.

Subject SGTPuzzler uses native methods to interact with
the underlying operating system. For it, we manually checked the possible
Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
annotations for it. 
Two subjects (MyTracks and Fennec)
use a customized pattern to interact with the GUI framework.
For them, we added \filternum user-defined filters, described in Section~\ref{sec:heuristic}.
In this experiment, none of the paper
authors was familiar with the subject programs, but we found it was quite easy
to add extra annotations and user-defined filters. All these
manual parts took less than a total of 60 minutes.

@@

\tinystep
%\vspace{1mm}
\subsection{Results}
\label{sec:results}

@@

\vspace{-1mm}
\subsubsection{Errors in Multithreaded GUI Applications}
\label{sec:errors}

As shown in Table~\ref{table:results}, our tool found
errors in each subject program. Using the 1-CFA
call graph algorithm, our tool issued \warnings warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown,
and the \oldbugs known errors were correctly identified),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

We submitted all \newbugs new errors to the respective developers. As of May 2012, 
1 error in S3dropbox has been confirmed, and we have reproduced all the other errors.
All found bugs and our experimental results are
publicly available at \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
%in which 2 errors in FileBunker and ArecaBackup
%have not yet been verified by the developers. 
%2 errors in SudokuSolver can be reproduced by simply
%clicking its UIs, and the rest 4 errors can be reproduced
%by writing a test driver have not yet been verified
%by the developers.

@@

77.private void deleteError() \ttlcb
78.    String text = "Cannot delete folder .....";
79.    display.showErrorMessage("Delete failed", 
        String.format(text, controller.getSelectedBucketName())); 
80.\ttrcb
\end{alltt}
\end{CodeOut}
\vspace*{-15pt}
\Caption{{\label{fig:swingerror} An
invalid thread access error reported by our tool
in the S3dropbox Swing application. The error occurs when
the method \CodeIn{deleteCurrentBucket} invoked on line 63 throws
an exception, which causes method \CodeIn{deleteError} to
access a Swing GUI object \CodeIn{display} on line 79 from
a non-UI thread. This error was previously unknown, and has been confirmed by the S3dropbox developers.
}} %\vspace{-1mm}
\end{figure}

@@

%\vspace{-4mm}
\subsubsection{Comparison to Requiring Wrappers}
\label{sec:straightforward}
